%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a modified ONE COLUMN version of
% the following template:
% 
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Shubham Raj}{}{ 
\href{mailto:shubham.raj.in@gmail.com}{shubham.raj.in@gmail.com} | 8449719965
}

\begin{center}
\huge\color{subheadings}\custombold{Software Developer}
\end{center}

\section{Experience}
\runsubsection{TREEBO HOTELS}
\descript{| Software Developer }
\runsubsection{}
\descript{TECH STACK - PYTHON (DJANGO, FLASK), POSTGRES}
\location{July 2017 – Present | Bengaluru}
\vspace{\topsep} % Hacky fix for awkward extra vertical space

\location{ Transformer Rewiring | Team size : 1}
\begin{tightemize}
\item Transformer was modified to adapt bookings from a new booking engine- CRS.
\item THSC client was integrated to interact with CRS. 
\end{tightemize}

\location{ Promotion Utility Enhancements | Team size : 1}
\begin{tightemize}
\item Upgraded the legacy platform application according business needs.
\item Made performance related optimizations.
\item Intelligence was added so that sell price due to applied promotion do not breach declared tariff.
\end{tightemize}

\location{ Inventory Throttling Service | Team size : 5}
\begin{tightemize}
\item In order to get control on the inventory we are selling the inventory was throttled with reference to certain rules.
\item Project was done in two parts Push and Pull.
\item APIs were written to pull inventory for channels that doesn’t support rule push feature.
\item My role : Flow from listening to the pushed rule queue to pushing the rule to Maximojo, including the validation and tracking metrics.
\end{tightemize}
\location{Travel Agent Automation | Team size : 2}
\begin{tightemize}
\item Objective was to automate the corporate booking flow, involving generation of partial payment links, reminding their payment and cancellation of booking if the customer haven’t paid upon reminders.
\item My role : Automation flow.
\end{tightemize}
\location{Search Engine Optimization | Team size : 3}
\begin{tightemize}
\item To get higher indexing in Google search results SEO pages were made and refactored for the company.
\item My role : Several data were added to the Meta API like : blogs, nearby landmarks, weather widget and map data.
\end{tightemize}
\location{Intelligent PAH Disable | Team size : 1}
\begin{tightemize}
\item To reduce no-show which PAH was mainly responsible for PAH was disabled depending upon certain metrics such as: occupancy at the time of booking, ABW and number of rooms booked by the customer.
\item All the configurations were highly configurable and the performance was audited for future reference.
\end{tightemize}
\location{Misc. | Team size : 1}
\begin{tightemize}
\item Several smaller projects were done: No- show bulk booking filter, Scraping web data, Bug fixes, Data migration scripts.
\end{tightemize}
\sectionsep

\runsubsection{ITRON PRIVATE LIMITED}
\descript{| R\&D Intern }
\location{June 2016 – July 2016 | Bengaluru}
\begin{tightemize}
\item Involved designing of an algorithm that estimates the optimal position of collectors and access  points of a wireless sensor network, taking in consideration of network constraints.
\item Used clustering techniques such as K-Means and MST.
\item Made UI for displaying the results on the map using XAML and Telerik RadMaps api. 
\end{tightemize}
\sectionsep

\runsubsection{SOLARWAALE}
\descript{| WEB DEVELOPER INTERN }
\location{June 2015 – July 2015 | Gurugram}
\begin{tightemize}
\item Developed an online portal displaying all the projects done by the company on an interactive map. The data was extracted from database and Google Maps api was used to realize the same.
\item Created dashboard that involved authentication for the customers.
\item Improvised the front page of the company.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}
\runsubsection{Indian Institute of Technology}
\descript{| B.TECH IN ELECTRONICS AND COMMUNICATION ENGINEERING}
\location{ May 2013 - May 2017| Roorkee, UK \textbullet{} CGPA: 6.4 / 10.0}
\sectionsep

\runsubsection{Delhi Public School}
\descript{| Science}
\location{ Batch of 2013 | Bokaro Steel City, JH}
X CGPA : 9.8/10.0 • XII CGPA : 89/100
\sectionsep


\section{Projects}
\runsubsection{AGRICULTURE INFORMATION SYSTEM}
\descript{| B.Tech Project}
\location{ July 2016 - May 2017 | Indian Institute of Technology, Roorkee}
\begin{tightemize}
\item Objective was to implement password hardening in the AIS authentication system.
\item JAVA application was made to implement the above by capturing behavioural biometrics such as : typing speed, inter key pattern to characterize each user.
\item Latter the characteristic adapted on every successful login.
\linebreak
\end{tightemize}
\sectionsep

\runsubsection{3D LASER SCANNER}
\descript{| SHRISTI 2014}
\location{ July 2015 - Dec 2015 | Indian Institute of Technology, Roorkee}
\begin{tightemize}
\item Objective was to create a 3D model of given specimen.
\item 3D laser scanner was made using line laser, a webcam, a stepper motor and an arduino.
\item The data collected was processed in matlab to generate a 3D model.
\linebreak
\end{tightemize}
\sectionsep


\section{LANGUAGES}

\begin{minipage}[t]{0.60\textwidth} 

\subsection{Programming}
\location{Over 5000 lines:}
Python \textbullet{}   Java \textbullet{} C\# \textbullet{} HTML \\
\location{Over 1000 lines:}
C++\textbullet{} CSS \textbullet{} PHP \textbullet{} JS \textbullet{} MySQL \textbullet{} \LaTeX\ \\
\location{Familiar:}
Android \textbullet{} MATLAB
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.30\textwidth} 

\subsection{SPOKEN \& WRITTEN}
\location{Native fluency:}
English, Hindi
\location{Reading fluency:}
Sanskrit
\sectionsep

\end{minipage} 

\sectionsep


\section{Extra curricular}
\runsubsection{Microsoft Code.fun.do}
\begin{tightemize}
\item{Actively participated and qualified four consecutive hackathon.}
\end{tightemize}
\sectionsep

\runsubsection{SPIC MACAY}
\descript{| IITR}
\begin{tightemize}
\item{Designed the official website of SPICMACAY IIT Roorkee Chapter.}
\item{Wincon 2015 : On December 2015 SPICMACAY IIT Roorkee chapter organised a 7 days convention Winter
national convention in which 1200 delegates from all over India came to witness the event. I being the part of the registration team was responsible for registering delegates, assigning them IDs and sending them regular emails related to event. These were done through Python scripts.}
\end{tightemize}
\sectionsep

\end{document}  \documentclass[]{article}