% Resume (English) — compiles to resumeEn.pdf
% Compile with: xelatex -interaction=nonstopmode resumeEn.tex
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
\documentclass[]{deedy-resume-openfont}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TITLE NAME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\lastupdated
\namesection{Shubham Raj}{}{
\href{mailto:shubham.raj.in@gmail.com}{shubham.raj.in@gmail.com} | +852 70733743
}

\begin{center}
\huge\color{subheadings}\custombold{KDB+ Developer | Quantitative Technology}
\end{center}

\noindent Director-level KDB+/q specialist with 8+ years of experience building low-latency tick plant infrastructure, real-time analytics, and AI-augmented trading systems across Morgan Stanley, UBS, and HSBC.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TECHNICAL SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Technical Skills}
\location{Core:} KDB+/q, Tick Architecture (RDB/HDB/TP/Gateway), IPC, qSQL, Functional Queries \\
\location{AI \& ML:} GitHub Copilot, LLM-assisted development, AI-based anomaly detection \& reconciliation \\
\location{Languages:} Python, Java, JavaScript (ReactJS), C\#, HTML/CSS, \LaTeX \\
\location{Infrastructure:} Docker, CI/CD Pipelines, RHEL, WebSocket, Kubernetes \\
\location{Tools:} KX Dashboard, KX Developer, Git, TeamCity
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{MORGAN STANLEY}
\descript{| Director}
\runsubsection{}
\descript{KDB+/Q | AI-ASSISTED DEVELOPMENT}
\location{January 2025 – Present | Hong Kong}
\vspace{\topsep}

\location{MSCL | Team size: 2}
\begin{tightemize}
\item Lead KDB+ developer at MSCL, responsible for maintaining and optimizing the tick plant infrastructure (TP, RDB, HDB, Gateway) and developing advanced real-time analytics solutions.
\item Leveraged AI-assisted development tools (GitHub Copilot, LLMs) to accelerate KDB+/q development, code reviews, and documentation—improving delivery velocity and code quality across the team.
\item Designed AI-based anomaly detection and reconciliation workflows on real-time tick data, providing CRB traders with actionable signals for risk management.
\item Enhanced the client IOI experience by introducing behavior-based IOIs and automating the H3 IOI process in collaboration with CRB traders, resulting in increased efficiency and more personalized client interactions.
\item Integrated a name server into the MSCL architecture for centralized system observability. Implemented a configuration manager to streamline MSCL configuration settings, improving system reliability.
\end{tightemize}
\sectionsep

\runsubsection{UBS}
\descript{| Authorised Officer}
\runsubsection{}
\descript{KDB+/Q, JAVASCRIPT (REACTJS), WEBSOCKET}
\location{February 2021 – December 2024 | Hong Kong}
\vspace{\topsep}

\location{Agency | Team size: 1}
\begin{tightemize}
\item Enhanced IOI accuracy to support Conditional VWAPs, GVWAPs, and GMOCs, managing an annual IOI notional volume of \$544 billion USD.
\item Optimized the Carbon commission system in partnership with facilitation and sales trading; onboarded Australia and refined selection logic. Tracked \$2.5B USD in facilitation trades and \$1.3B USD in follow-ons.
\item Expanded market-making IOIs to the EMEA region. Built a real-time interface using WebSocket protocol and ReactJS.
\item Introduced super-group mapping to consolidate IOIs sent to the same clients under different entity names.
\end{tightemize}

\location{Principal | Team size: 2}
\begin{tightemize}
\item Collaborated with the APAC Quants team to integrate a Python-based ML predictor (via embedPy) that generated trading signals for the CRB quote generator.
\item Rolled out Rhodium for Australia, Taiwan, and Japan to enable CRB internalisation across APAC.
\end{tightemize}

\location{GCA Core | Team size: 1}
\begin{tightemize}
\item Migrated GCA-APAC applications to RHEL 7 with core library upgrades; built CI pipelines replacing TeamCity for seamless automated builds.
\item Containerised GCA KDB+ applications using Docker, bringing the platform to a cloud-ready state.
\item Completed AC5 and Log4j security remediations across the GCA stack.
\end{tightemize}
\sectionsep

\runsubsection{LUXOFT}
\descript{| KDB+ Developer}
\runsubsection{}
\descript{KDB+/Q, KX TOOLS}
\location{April 2020 – February 2021 | Bengaluru}
\vspace{\topsep}

\location{Automated Trade Surveillance | Team size: 15}
\begin{tightemize}
\item Led a team of 5 KDB+ developers and coordinated with FD and TCS to deliver trade surveillance algorithms on schedule.
\item Developed and refactored post-trade alert algorithms (TOOB, UTV, UTPM) that evaluated trades against configurable benchmarks and compliance rules.
\item Consistently met sprint targets with measurable improvement in team burn-down velocity.
\end{tightemize}
\sectionsep

\runsubsection{HSBC ELECTRONIC DATA PROCESSING INDIA PVT LTD}
\descript{| Associate}
\runsubsection{}
\descript{KDB+/Q, PYTHON, JAVASCRIPT}
\location{June 2018 – April 2020 | Bengaluru}
\vspace{\topsep}

\location{THOR Stress Test Integration | Team size: 2}
\begin{tightemize}
\item Built the stress testing module for HSBC's execution algorithm back-tester (THOR). Fetched Reuters historical data via TRTH API, persisted to disk, and rewired THOR to the new data source.
\item Developed TCAs to compare simulation outputs—uncovered a critical bug in the QDAP liquidity-seeking model that could have led to over-execution.
\end{tightemize}

\location{Market Microstructure | Team size: 1}
\begin{tightemize}
\item Computed daily and monthly market statistics from historical KDB+ databases; designed a load-balancer with a caching layer and HTML frontend for sales traders.
\item Provided an orthogonal view enabling traders to identify patterns across indexes and individual tickers over time.
\end{tightemize}

\location{BACCS \& Report Utility | Team size: 2}
\begin{tightemize}
\item Centralised the capital commission system (BACCS) with user authentication, ticker onboarding, risk book management, and PnL calculations.
\item Built an asynchronous report utility using a publisher-subscriber model with LDAP authentication, unifying quant reports across the desk.
\end{tightemize}
\sectionsep

\runsubsection{TREEBO HOTELS}
\descript{| Software Developer}
\runsubsection{}
\descript{PYTHON (DJANGO, FLASK), POSTGRESQL}
\location{June 2017 – June 2018 | Bengaluru}
\begin{tightemize}
\item Built an inventory throttling service that controlled OTA channel distribution based on configurable business rules.
\item Automated the corporate booking flow—partial payment link generation, payment reminders, and auto-cancellation for overdue bookings.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}
\runsubsection{Indian Institute of Technology, Roorkee}
\descript{| B.TECH IN ELECTRONICS AND COMMUNICATION ENGINEERING}
\location{May 2013 – May 2017 | Roorkee, Uttarakhand}
\sectionsep

\runsubsection{Delhi Public School}
\descript{| Science}
\location{Batch of 2013 | Bokaro Steel City, Jharkhand}
X: 98\% \textbullet{} XII: 89\%
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LANGUAGES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Languages}

\subsection{Spoken \& Written}
English (Native) \textbullet{} Hindi (Native) \textbullet{} Sanskrit (Reading)
\sectionsep

\end{document}
